---
title: "Developing Data Products - Assignment 4 Home Value Calculator"
author: "bjpotrat"
date: "8/19/2019"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

During the course of owning a home, owners often wonder how much a home remodel or addition will affect the value of their home.

With the "Home Value Calculator" App, users can upload a .csv file with information from Zillow.com, Redfin.com, or the user's county parcel map.

Please note that the Load Data and Calculate button will load a test dataset. 

## Initial Linear Model Applied and Data Cleaning


When applying an initial linear model the test dataset, some components of the home have negative coeffients which doesnot make a lot of sense.  However, the initial linear does generate a good method of cleaning the data of outliers for alternative model generation.

```{r echo=FALSE}
Housedata <-read.csv(url('https://github.com/bjpotrat/DevDataProdsAsn4/raw/master/Housedata.csv'))
mdl.lm <- lm(BuildingValue~Beds+Bath50+Bath75+Bath100+Kitchens+TotalSqft+Fireplace+0, data= Housedata)
mdl.lm$coefficients
```
```{r echo=FALSE, fig.align='center', out.width = '40%'}
cooksd <- cooks.distance(mdl.lm)
plot(cooksd, pch="*", cex=2, main="Influential Obs by Cooks distance")
abline(h =mean(cooksd, na.rm=T), col="red")
text(x=1:length(cooksd)+1, y=cooksd, labels=ifelse(cooksd>mean(cooksd, na.rm=T),names(cooksd),""), col="red")
influential <- as.numeric(names(cooksd)[(cooksd > mean(cooksd, na.rm=T))])
```

## Non-Negative Linear Model (NNLM)
Using NNLM, the coefficients of a linear model are forced to be possitive.  The square footage of the home had to be scaled by a factor of 1000 to prevent abnormal wieght of it's coefficient.
```{r echo=FALSE}
library(NNLM)
Housedata.Clean<-Housedata[-influential,]
x<-Housedata.Clean[c("Beds","Bath50","Bath75","Bath100","Kitchens","TotalSqft","Fireplace")]
y<-Housedata.Clean["BuildingValue"]
mdl.NNLM <- nnlm(data.matrix(x),y, method = "lee", loss = "mse", alpha = 20)
round(mdl.NNLM$coefficients,2)
```

```{r, echo=FALSE, fig.align='center', out.width = '40%'}
yhat<- data.matrix(x) %*% as.vector(t(mdl.NNLM$coefficients[,1]))
nnlm.residuals<-t(y-yhat)
barplot(nnlm.residuals, main = "Residuals from NNLm")
abline(h=c(-100000,-50000,0,50000,100000), col="gray", lty=2)
```

## Using the App 
User Interaction:

- The user can load or calculate the by "clicking data and calclulate".

- The user can select their home's Id, which can be found on the House Data tab after the data has been loaded and calculated.

- The user can have the app calculate the estimated value of a house by clicking "Estimate Home Improvements".

- The user can download and upload thier own data by using the download Homedata.csv and upload Homedata.csv button.

Output data tabs feature:

- The models estimated values verse the housedata.csv's values.

- Your current home's value base on "Your home's ID"

- Your estimated home's value based on the selected home parameters

- House Data Loaded

- The model coefficients generated from NNLM
